---
title: "Bootstrapping"
author: "Kylie Wheelock Riley"
date: "11/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```
 
2 simulated datasets. 
both use simple linear regressions, but they are different.

The variance in dataset 2 is not constant. so the assumptions in linear regression are not kept
```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

fit 2 models
```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

sim_df_nonconst %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

## how can I bootstrap?
write a function to draw a bootstrap sample based on a dataframe
```{r}
##Will still get a dataset of size 250, but each one will be different. 
##Have a dataset, take a sample from the dataset by pulling 1 observation at a time. 

boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

```{r}
boot_sample(df = sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point(alpha = 0.5)
```

Making a dataframe of the bootstraps
```{r}
boot_straps =
  tibble(stramp_num = 1:1000,
         strap_sample = rerun(1000, boot_sample(df = sim_df_nonconst))
         )
boot_straps
```

Want to do some kind of analysis.
Will to look at the slope (maybe intercept?) Should not be the same of the default.  Will fit linear models to each bootstrap output. 
```{r}
bootstrap_results = 
boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results)
```

summarize these results
```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))
```

## Try the modelr package
just did bootstrapping by hand, but there is a function that can help with it. 
Do not have to use bootstraping function on modelr, but it is easier and if you do you should know that in the background it is sampling with replacement each time. 
```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))

```

## What if your assumptions aren't wrong?
```{r, include = FALSE}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()

sim_df_const %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)
         ) %>% 
  ##select(-models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

## Revisiting airbnb data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point() 
```

re-use the stuff we just did
```{r}
nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  models = map(strap, ~ lm(price ~ stars + room_type, data = .x))
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()
  
```

