---
title: "linear_models"
author: "Kylie Wheelock Riley"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Consider price as an outcome that may depend on rating and borough. We fit that initial model in the following code.
```{r}
##outcome = price
##predictors = stars and boro
fit = lm(price ~ stars + boro, data = nyc_airbnb)
fit
##boro is categorical.  R makes it a factor, and default orders alphabetically. In the model above the bronx is the reference group. 
```

```{r}
##gives additional information on fit, more than just "fit"
summary(fit)

##extract coefficients
coef(fit)
summary(fit)$coef

```

Tidy results
```{r}
fit %>% 
  broom::tidy() %>% 
  ##code below tidys up "term" var for showing results
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```

##Take a look at factors
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  ##putting categorical variables in order of how often they appear in the dataset with fct_infreq
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```

refit the model
```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()

fit %>% 
  broom::glance()
```

##Diagnostics
```{r}
##spits out dataframes that are ammenable to other things that we want to do
##adds residuals so that you can plot them
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) +
  geom_violin() +
  ylim(-500, 500)

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  ylim(-500, 500)


##fitted values in the modelr package
modelr::add_predictions(nyc_airbnb, fit)
```

##Hypothesis testing
```{r}
##fitting a null and alternative hypthesis
##skipped over in class, maybe too detailed for what we need, but it does exist
fit_null = lm(price ~ stars + boro, data = nyc_airbnb)
fit_alt = lm(price ~ stars + boro + room_type, data = nyc_airbnb)
```

##Nesting
```{r}
##fitting an interaction terms]
fit_interaction = lm(price ~ stars * boro + room_type * boro, data = nyc_airbnb)

fit_interaction %>%
  broom::tidy()
##output shows that in manhattan you are going to be paying more for addtional star ratings.  Not as much in bk and bx. (star rating has no association with price)


```

```{r}
##easier to understand collection of coefficients. Tells you what the effect is only in BK. 

nyc_airbnb %>% 
  filter(boro == "Brooklyn") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

Lets try to map instead
```{r}
manhattan_airbnb =
  nyc_airbnb %>% 
  filter(boro == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb %>% 
  nest(data = -neighborhood) %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest(models)
```

Nesting neighborhoods
```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


Nesting works in some ways and not in others. If you are going to do a formal analysis a mixed model would work better, but we are not going to cover that now. 
Can fit things with binary outcomes instead of continuous. 













