---
title: "linear_models"
author: "Kylie Wheelock Riley"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

## Model Fitting 
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Price predicted by rating and borough.
```{r}

fit = lm(price ~ stars + boro, data = nyc_airbnb)

```
In the model above, boro is categorical.  R makes categorical variables a factor, and the default ordering is alphabetical. This makes the bronx the reference group. 

## Tidying Output

To look at the output of the models you can use the code below:
```{r}
##gives additional information on fit, more than just "fit"
summary(fit)


##extract coefficients
coef(fit)
summary(fit)$coef

## fitted.values(fit)
## The one above gives a really long output!
```

To make the results more presentable you can tidy them.  The functions below also produce data frames, which makes it straightforward to include the results in subsequent steps.
```{r}
fit %>% 
  broom::glance() 

fit %>% 
  broom::tidy() %>% 
  ##code below tidys up "term" var for showing results
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```

Reordering Factors: 
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  ##putting categorical variables in order of how often they appear in the dataset with fct_infreq
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```

refit the model
```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()

fit %>% 
  broom::glance()
```

## Diagnostics
The modelr package can be used to add residuals and fitted values to a dataframe. 
```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) +
  geom_violin() +
  ylim(-500, 500)

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  ylim(-500, 500)


##fitted values in the modelr package
modelr::add_predictions(nyc_airbnb, fit)
```

## Hypothesis testing

Fit a basic and more complex model, then compare the outcomes using an ANOVA. 
ONLY WORKS FOR NESTED MODELS.
```{r}
fit_null = lm(price ~ stars + boro, data = nyc_airbnb)
fit_alt = lm(price ~ stars + boro + room_type, data = nyc_airbnb)
```

```{r}
anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

## Nesting Data
Fitting models to datasets nested within variables – meaning, we’ll use nest to create a list column containing datasets and fit separate models to each.
```{r}
nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

We can nest within boroughs and fit borough-specific models associating price with rating and room type:
```{r}
nest_lm_res =
  nyc_airbnb %>% 
  nest(data = -boro) %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest(models)

nest_lm_res %>% 
  select(boro, term, estimate) %>% 
  mutate(term = fct_inorder(term)) %>% 
  pivot_wider(
    names_from = term, values_from = estimate) %>% 
  knitr::kable(digits = 3)
```

Fitting models to nested datasets is a way of performing stratified analyses. These have a tradeoff: stratified models make it easy to interpret covariate effects in each stratum, but don’t provide a mechanism for assessing the significance of differences across strata.

Fitting model for Manhattan only
```{r}
manhattan_airbnb =
  nyc_airbnb %>% 
  filter(boro == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb %>% 
  nest(data = -neighborhood) %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest(models)
```

```{r}
##fitting an interaction terms
fit_interaction = lm(price ~ stars * boro + room_type * boro, data = nyc_airbnb)

fit_interaction %>%
  broom::tidy()
##output shows that in manhattan you are going to be paying more for addtional star ratings.  Not as much in bk and bx. (star rating has no association with price)


```

```{r}
##easier to understand collection of coefficients. Tells you what the effect is only in BK. 

nyc_airbnb %>% 
  filter(boro == "Brooklyn") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

Nesting neighborhoods
```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


Nesting works in some ways and not in others. If you are going to do a formal analysis a mixed model would work better, but we are not going to cover that now. 
Can fit things with binary outcomes instead of continuous. 